---
title: "HomeOffice_Main_Analysis"
author: "Marton Kovacs"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: 
  word_document: default
  html_document: default
---

# Install packages

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
```

# Source R scripts

```{r}
r_scripts <- list.files("R/", full.names = TRUE)
walk(r_scripts, source)
```

# Importing data

```{r, message = FALSE}
processed <- read_tsv("Data/Main/Processed/HomeOffice_Main_Processed_data.tsv")
```

# Descriptives
## Number of respondents

There are `r nrow(processed)` individual responses used for the analysis.

## Median time of responding to the survey

```{r}
processed %>% 
  mutate(duration_in_seconds = as.integer(duration_in_seconds)) %>% 
  summarise(median_resp = median(duration_in_seconds) / 60)
```

# Background information
## Data preprocessing

Variables that we will use to create the subgroups for the background information.

```{r}
subvars <- c("position", "area_of_research", "wokrplace_type", "data_coll_remote", "gender", "age", "edu_duties", "team_work", "partner_work", "living_sit", "homeschool", "childcare_help", "work_home_dist", "office_setup", "number_of_children")
```

We transform all the background information questions to character and replace NAs with "not applicable". We will use these as subgroup labels only in the following.

```{r}
processed <-
  processed %>% 
  mutate_at(all_of(subvars),
            as.character) %>% 
  mutate_at(all_of(subvars),
            replace_na, "not applicable")
```

Calculating the counts and proportions of each subgroup.
_note: There is a position NA subgroup which was not an answer option in the survey but based on one respondents comment we dropped his answer to this question._

```{r}
background_inf <-
  tibble(subvars = subvars) %>% 
  mutate(subgroup_desc = purrr::map(subvars, subgroup_count)) %>% 
  select(subvars, subgroup_desc) %>% 
  unnest(subgroup_desc) %>% 
  select(-N) %>% 
  mutate(subvars = case_when(subvars == "position" ~ "Academic position",
                             subvars == "area_of_research" ~ "Area of research",
                             subvars == "wokrplace_type" ~ "Workplace type",
                             subvars == "data_coll_remote" ~ "Data collection remotely",
                             subvars == "gender" ~ "Gender",
                             subvars == "age" ~ "Age",
                             subvars == "edu_duties" ~ "Educational duties",
                             subvars == "team_work" ~ "Team work",
                             subvars == "partner_work" ~ "Partner working",
                             subvars == "living_sit" ~ "Living situation",
                             subvars == "homeschool" ~ "Homeschooling",
                             subvars == "childcare_help" ~ "Help with childcare",
                             subvars == "work_home_dist" ~ "Work-home distance",
                             subvars == "office_setup" ~ "Home office setup",
                             subvars == "number_of_children" ~ "Number of children")) %>% 
  rename(`Background information question` = subvars,
         Subgroups = levels,
         `Number of responses` = n,
         `Proportion of the subgroup` = prop)
```

```{r}
papaja::apa_table(
  background_inf,
  caption = "A Full Summary of All Background Information",
  escape = TRUE
)
```

```{r}
map(subvars, ~ apa_barplot(processed, .x))
```

# Percentage of working more from home during the pandemic

```{r}
percent_by_group(processed, working_home_time)
```

`r filter(processed, working_home_time == "Yes") %>% count()` researchers worked more from home during the pandemic lockdown.

# Efficiency of remote working
## During the lockdown

```{r}
processed %>% 
  distinct(now_before_eff)

now_before_eff_data <-
  processed %>% 
  filter(working_home_time == "Yes")

now_before_eff_desc <-
  now_before_eff_data %>% 
  percent_by_group(now_before_eff)

now_before_eff_desc
```

The number of trials where the efficiency rating is missing is `r filter(processed, is.na(now_before_eff)) %>% count() %>% pull(n)`. It is because this question was not shown to those who said that they are not working more from home.

`r filter(now_before_eff_desc, now_before_eff == "less efficient") %>% pull(prop)`% of the surveyed scientists who worked more from home during the coronavirus lockdown found that due to working more from home their research became, in general, less efficient, `r filter(now_before_eff_desc, now_before_eff == "more efficient") %>% pull(prop)`% found it more efficient, and `r filter(now_before_eff_desc, now_before_eff == "similarly efficient") %>% pull(prop)`% found no difference compared to working before the lockdown. (only from those working from home).

```{r}
y_max_during <- round_any(max(now_before_eff_desc$prop), 10, f = ceiling)

now_before_eff_plot <- 
  now_before_eff_desc %>% 
  mutate(label = glue::glue("{n} / {N}"),
         now_before_eff = stringr::str_to_title(now_before_eff),
         now_before_eff = forcats::fct_relevel(now_before_eff, c("Less Efficient", "Similarly Efficient", "More Efficient"))) %>% 
  ggplot() +
  aes(x = now_before_eff,
      y = prop) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = label), vjust = -0.2, size = 8) +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, y_max_during),
                     label = scales::label_percent(scale = 1)) +
  labs(x = "Change in the Efficiency of the Research Work",
        y = "Percentage of Responses") +
  papaja::theme_apa() +
  theme(axis.title = element_text(size = 20),
        axis.text = element_text(size = 15))

now_before_eff_plot
```

## After the lockdown

```{r}
processed %>% 
  distinct(now_later_eff)

now_later_eff_data <-
  processed %>% 
  filter(prior_home_prop_1 != 100)

now_later_eff_desc <-
  now_later_eff_data %>%
  percent_by_group(now_later_eff)

now_later_eff_desc
```

The number of trials where the efficiency rating is missing is `r filter(processed, is.na(now_later_eff)) %>% count() %>% pull(n)`. It is because the respondent did not understand the question as she stated in the comments. However, she said that she used to work 100% before the lockdown from home, therefore her rating will not be included in the analysis anyway.

The number of respondents whose response was excluded because they used to work 100% from home before the lockdown: `r filter(processed, prior_home_prop_1 == 100) %>% count() %>% pull(n)`

`r filter(now_later_eff_desc, now_later_eff == "less efficient") %>% pull(prop)`% of the surveyed scientists assume that working more from home after the coronavirus lockdown could make their research, in general, less efficient, `r filter(now_later_eff_desc, now_later_eff == "more efficient") %>% pull(prop)`% found it more efficient, and `r filter(now_later_eff_desc, now_later_eff == "similarly efficient") %>% pull(prop)`% found no difference compared to the time before the lockdown. (excluding 100% home workers).

```{r}
y_max_after <- round_any(max(now_later_eff_desc$prop), 10, f = ceiling)

now_later_eff_plot <- 
  now_later_eff_desc %>%
  mutate(label = glue::glue("{n} / {N}"),
         now_later_eff = stringr::str_to_title(now_later_eff),
         now_later_eff = forcats::fct_relevel(now_later_eff, c("Less Efficient", "Similarly Efficient", "More Efficient"))) %>% 
  ggplot() +
  aes(x = now_later_eff,
      y = prop) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = label), vjust = -0.2, size = 5) +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, y_max_after),
                     label = scales::label_percent(scale = 1)) +
  labs(x = "Change in the efficiency of the research work",
        y = "Percentage of responses") +
  papaja::theme_apa() +
  theme(axis.title = element_text(size = 20),
        axis.text = element_text(size = 15))

# Save for the paper
ggsave("Figures/Fig1.tiff", device = "tiff", plot = now_later_eff_plot, dpi = 300, width = 208, height = 118, units = "mm")

# Save for the manuscript
ggsave("Figures/Fig1.png", device = "png", plot = now_later_eff_plot, dpi = 300, width = 208, height = 118, units = "mm")

now_later_eff_plot
```

## Investigating aspects of research

We calculate the means and SDs of each aspects ratings. Aspects with higher rating than 4 indicates that it is better to do the task from the lab. Ratings with lower mean rating than 4 means that it is better to do the given action from home.

_note: Based on one comment we dropped the aspect ratings of one respondent during data processing._

```{r, message = FALSE}
aspects <- 
  processed %>%
  filter_at(
    vars(contains("home_office_aspect")),
    all_vars(!is.na(.))) %>% 
  select(participant_id, contains("home_office_aspect")) %>%
  gather(key = "aspect", value = "rating", -participant_id) %>% 
  mutate(aspect = case_when(aspect == "home_office_aspect_1" ~ "Optimally organizing my time",
                            aspect == "home_office_aspect_2" ~ "Optimally organizing my tasks",
                            aspect == "home_office_aspect_3" ~ "Keeping focused on my tasks",
                            aspect == "home_office_aspect_4" ~ "Keeping in touch with my team",
                            aspect == "home_office_aspect_5" ~ "Sharing thoughts with colleagues",
                            aspect == "home_office_aspect_6" ~ "Getting support from colleagues",
                            aspect == "home_office_aspect_7" ~ "Working on my manuscript",
                            aspect == "home_office_aspect_8" ~ "Analyzing my data",
                            aspect == "home_office_aspect_9" ~ "Reading the literature",
                            aspect == "home_office_aspect_10" ~ "Collecting data",
                            aspect == "home_office_aspect_11" ~ "Having the infrastructure\n(IT, books, instruments)",
                            aspect == "home_office_aspect_12" ~ "Maintaining emotional balance",
                            aspect == "home_office_aspect_13" ~ "Maintaining work-life balance",
                            aspect == "home_office_aspect_14" ~ "Keeping good relationship\nwith colleagues",
                            aspect == "home_office_aspect_15" ~ "Developing new skills")) %>% 
  group_by(aspect) %>% 
  summarise(mean = round(mean(rating, na.rm = TRUE), 2),
            sd = round(sd(rating, na.rm = TRUE), 2)) %>% 
  mutate(better_home = case_when(mean > 4 ~ 0L,
                                 mean < 4 ~ 1L,
                                 mean == 4 ~ NA_integer_)) %>% 
  arrange(better_home, mean)
```

```{r}
aspects_plot <- 
  aspects %>%
  ggplot() +
  aes(x = fct_reorder(aspect, mean),
      y = mean) +
  geom_bar(stat = "identity") +
  scale_y_continuous(
    expand = c(0, 0.4),
    breaks = c(1, 2, 3, 4, 5, 6, 7),
    labels = c("1\nAt Home", "2", "3", "4", "5", "6", "7\nIn the Office")) +
  coord_flip(ylim = c(1, 7)) +
  geom_hline(yintercept = 4, linetype = "dashed", color = "#828282", size = 2) +
  # geom_text(aes(label = as.character(mean)), size = 8, hjust = - 0.3) +
  labs(x = "Aspects",
        y = "Mean rating") +
  papaja::theme_apa() +
  theme(axis.title = element_text(size = 20),
        axis.text = element_text(size = 15),
        plot.margin = unit(c(.5, .5, .5, .5), "cm"))

# Save for the paper
ggsave("Figures/Fig2.tiff", device = "tiff", plot = aspects_plot, dpi = 300, width = 308, height = 208, units = "mm")

# Save for the manuscript
ggsave("Figures/Fig2.png", device = "png", plot = aspects_plot, dpi = 300, width = 308, height = 208, units = "mm")

aspects_plot
```

### Main advantages of working from home

The three lowest-rated advantages of working from home

```{r}
aspects %>% 
  filter(better_home == 1L) %>% 
  slice_min(mean, n = 3)
```

### Main advantages of working in the lab

The three highest-rated advantages of working from the lab

```{r}
aspects %>% 
  filter(better_home == 0L) %>% 
  slice_max(mean, n = 3)
```

## How much did researchers work from home before the pandemic?

The distribution of percentages of working from your home time before the pandemic.

```{r}
percentage_plot_data <-
    processed %>%
    select(participant_id,
           prior_home_prop_1,
           future_home_prop_1) %>%
    gather(key = "time", value = "percent", -participant_id) %>%
    mutate(time = case_when(time == "prior_home_prop_1" ~ "Prior to pandemic",
                            time == "future_home_prop_1" ~ "Ideal"),
           time = factor(time, c("Prior to pandemic", "Ideal")))

percentage_plot_data %>%
  filter(time == "Prior to pandemic") %>% 
  ggplot() +
  aes(x = percent) +
  geom_density(alpha = 0.6, size = 0.8) +
  scale_y_continuous(expand = c(0.01, 0),
                     breaks = scales::pretty_breaks()) +
  scale_x_continuous(expand = c(0, 0),
                     breaks = seq(0, 100, 10),
                     labels = scales::label_percent(scale = 1)) +
  labs(x = "Percentage of worktime working from home prior to pandemic",
       y = "Density") +
  papaja::theme_apa() +
  theme(axis.title = element_text(size = 20),
        axis.text = element_text(size = 15))
```

## How much would researchers work from home after the pandemic?

The distribution of percentages of ideal working from home time after the pandemic.

```{r}
percentage_plot_data %>%
  filter(time == "Ideal") %>% 
  ggplot() +
  aes(x = percent) +
  geom_density(alpha = 0.6, size = 0.8) +
  scale_y_continuous(expand = c(0.01, 0),
                     breaks = scales::pretty_breaks()) +
  scale_x_continuous(expand = c(0, 0),
                     breaks = seq(0, 100, 10),
                     labels = scales::label_percent(scale = 1)) +
  labs(x = "Percentage of worktime working from home",
       y = "Density") +
  papaja::theme_apa() +
  theme(axis.title = element_text(size = 20),
        axis.text = element_text(size = 15))
```

Prior and ideal percentages of working from home on the same figure.

```{r}
percentage_plot <-
  percentage_plot_data %>%
  ggplot() +
  aes(x = percent,
      color = time) +
  geom_density(alpha = 0.6, size = 0.8) +
  scale_y_continuous(expand = c(0.01, 0),
                     breaks = scales::pretty_breaks()) +
  scale_x_continuous(expand = c(0, 0),
                     breaks = seq(0, 100, 10),
                     labels = scales::label_percent(scale = 1)) +
  scale_fill_manual(values = c('#000000', '#D3D3D3')) +
  scale_color_manual(values=c('#000000', '#D3D3D3'))+
  labs(x = "Percentage of worktime working from home",
       y = "Density",
       color = "Time") +
  papaja::theme_apa() +
  theme(axis.title = element_text(size = 20),
        axis.text = element_text(size = 15),
        legend.position = c(.8, .9),
        legend.title = element_blank(), 
        legend.text = element_text(size = 18),
        plot.margin = unit(c(1, 1, 1, 1), "cm"))

# Save for the paper
ggsave("Figures/Fig3.tiff", device = "tiff", plot = percentage_plot, dpi = 300, width = 308, height = 208, units = "mm")

# Save for the manuscript
ggsave("Figures/Fig3.png", device = "png", plot = percentage_plot, dpi = 300, width = 308, height = 208, units = "mm")

percentage_plot
```

## Would it be possible to work more from home in the future?

See the distinct values of the difference between the ideal percentage of working more from the future and the prior percentage. If the difference is negative the respondent wants to work less from home in the future, if it is positive the respondents wants to work more from home in the future.

```{r, eval = FALSE}
processed %>% 
  distinct(future_prior_diff) %>% 
  arrange(future_prior_diff) %>% 
  knitr::kable()
```

Showing a descriptive comparison.

```{r}
processed %>% 
  mutate(more_from_home = case_when(future_prior_diff > 0 ~ "Respondent wants to work more from home",
                                    future_prior_diff < 0 ~ "Respondent wants to work less from home",
                                    future_prior_diff == 0 ~ "Respondent working the ideal amount of time from home")) %>% 
  count(more_from_home) %>%
  mutate(N = sum(n),
         prop = n / N * 100) %>% 
  arrange(n)
```

Number of respondents who worked 100% from home before the pandemic.

```{r}
processed %>% 
  filter(prior_home_prop_1 == 100) %>% 
  count()
```

Taken all their other duties (education, administration, etc.) and provided circumstances at home (infrastructure, level of disturbance) of researchers think that it would be possible to work more from home in the future. (excluding 100% home workers, including only wishing to work more from home)

This sentence was preregistered: _OF those who find working from home more efficient_, but we left this filter out from the analysis.

```{r}
processed %>% 
  filter(prior_home_prop_1 != 100,
         future_prior_diff > 0
         # now_later_eff == "more efficient"
         ) %>% 
  count(feasible) %>% 
  mutate(N = sum(n),
         prop = n / N * 100)
```

## Additional analyses

Additional descriptive results will be provided for the interested subgroups.

### Are people living with children more or less efficient when working from home?

```{r}
processed %>% distinct(living_sit)

living_sit_include <- c("Living with partner and non-adult child(ren)", "Single-parent with non-adult child(ren)")
```

Number of kids in this subsample.

```{r}
now_before_eff_data %>% 
  filter(living_sit %in% living_sit_include) %>% 
  count(number_of_children)
```

Efficiency ratings during the pandemic.

```{r}
now_before_eff_data %>% 
  filter(living_sit %in% living_sit_include) %>% 
  percent_by_group(now_before_eff)
```

Efficiency ratings after the pandemic.

```{r}
now_later_eff_data %>% 
  filter(living_sit %in% living_sit_include) %>% 
  percent_by_group(now_later_eff)
```

### What circumstances make a researcher with children more or less efficient in working from home AFTER the lockdown?
#### With partner

```{r}
now_later_eff_data %>% 
  filter(living_sit == "Living with partner and non-adult child(ren)") %>% 
  percent_by_group(now_later_eff)
```

#### Single

```{r}
now_later_eff_data %>% 
  filter(living_sit == "Single-parent with non-adult child(ren)") %>% 
  percent_by_group(now_later_eff)
```

### What circumstances make a researcher with children more or less efficient in working from home DURING the lockdown?
#### With partner

```{r}
now_before_eff_data %>% 
  filter(living_sit == "Living with partner and non-adult child(ren)") %>% 
  percent_by_group(now_before_eff)
```

#### Single

```{r}
now_before_eff_data %>% 
  filter(living_sit == "Single-parent with non-adult child(ren)") %>% 
  percent_by_group(now_before_eff)
```

### Which subgroup would benefit the most/less from working more from home?
#### During

Using only the filtered dataset for the efficiency rating calculations.

```{r}
subgroup_eff_during <-
  tibble(subvars = subvars) %>% 
  mutate(levels = purrr::map(subvars,
                             ~ get_levels(
                               df = now_before_eff_data,
                               var = .x)),
         levels_eff = purrr::map2(subvars, levels,
                                         ~ efficiency_subgroups_levels(
                                           df = now_before_eff_data,
                                           subvar_name = .x,
                                           subgroup_name = .y,
                                           efficiency_var = now_before_eff)),
         levels_eff = set_names(levels_eff, map(subvars, ~rlang::as_name(.x)))) %>%
  select(subvars, levels_eff) %>% 
  unnest_longer(levels_eff) %>% 
  unnest(levels_eff) %>% 
  mutate(subvars = case_when(subvars == "position" ~ "Academic position",
                             subvars == "area_of_research" ~ "Area of research",
                             subvars == "wokrplace_type" ~ "Workplace type",
                             subvars == "data_coll_remote" ~ "Data collection remotely",
                             subvars == "gender" ~ "Gender",
                             subvars == "age" ~ "Age",
                             subvars == "edu_duties" ~ "Educational duties",
                             subvars == "team_work" ~ "Team work",
                             subvars == "partner_work" ~ "Partner working",
                             subvars == "living_sit" ~ "Living situation",
                             subvars == "homeschool" ~ "Homeschooling",
                             subvars == "childcare_help" ~ "Help with childcare",
                             subvars == "work_home_dist" ~ "Work-home distance",
                             subvars == "office_setup" ~ "Home office setup",
                             subvars == "number_of_children" ~ "Number of children")) %>% 
  select(subvars, levels_eff_id, now_before_eff, n, N, prop) %>%
  rename(`Background information question` = subvars,
         Subgroups = levels_eff_id,
         `Efficiency ratings` = now_before_eff,
         `Number of responses to the efficiency ratings` = n,
         `Number of respondents in the subgroup` = N,
         `Proportion of the subgroup` = prop)
```

```{r}
papaja::apa_table(
  subgroup_eff_during,
  caption = "Efficiency Ratings by Each Subgroup Comparing Efficiency Before and During the Lockdown",
  escape = TRUE
)
```

#### After

```{r}
subgroup_eff_later <-
  tibble(subvars = subvars) %>% 
  mutate(levels = purrr::map(subvars,
                             ~ get_levels(
                               df = now_later_eff_data,
                               var = .x)),
         levels_eff = purrr::map2(subvars, levels,
                                         ~ efficiency_subgroups_levels(
                                           df = now_later_eff_data,
                                           subvar_name = .x,
                                           subgroup_name = .y,
                                           efficiency_var = now_later_eff)),
         levels_eff = set_names(levels_eff, map(subvars, ~rlang::as_name(.x)))) %>%
  select(subvars, levels_eff) %>% 
  unnest_longer(levels_eff) %>% 
  unnest(levels_eff) %>% 
  mutate(subvars = case_when(subvars == "position" ~ "Academic position",
                             subvars == "area_of_research" ~ "Area of research",
                             subvars == "wokrplace_type" ~ "Workplace type",
                             subvars == "data_coll_remote" ~ "Data collection remotely",
                             subvars == "gender" ~ "Gender",
                             subvars == "age" ~ "Age",
                             subvars == "edu_duties" ~ "Educational duties",
                             subvars == "team_work" ~ "Team work",
                             subvars == "partner_work" ~ "Partner working",
                             subvars == "living_sit" ~ "Living situation",
                             subvars == "homeschool" ~ "Homeschooling",
                             subvars == "childcare_help" ~ "Help with childcare",
                             subvars == "work_home_dist" ~ "Work-home distance",
                             subvars == "office_setup" ~ "Home office setup",
                             subvars == "number_of_children" ~ "Number of children")) %>% 
  select(subvars, levels_eff_id, now_later_eff, n, N, prop) %>%
  rename(`Background information question` = subvars,
         Subgroups = levels_eff_id,
         `Efficiency ratings` = now_later_eff,
         `Number of responses to the efficiency ratings` = n,
         `Number of respondents in the subgroup` = N,
         `Proportion of the subgroup` = prop)
```

```{r}
papaja::apa_table(
  subgroup_eff_later,
  caption = "Efficiency Ratings by Each Subgroup Comparing Efficiency During and After the Lockdown",
  escape = TRUE
)
```

### Would it be ideal and possible for those with teaching duties to work proportionally more from home in the future than before the pandemic?

Even among those who have teaching duties at work, xx% think that more working from home would be ideal,  and possible and their work would be more efficient.

```{r}
processed %>%
  filter(
    prior_home_prop_1 != 100,
    future_prior_diff > 0,
         # now_later_eff == "more efficient",
         edu_duties == "Yes"
    ) %>%
  group_by(edu_duties) %>% 
  count(feasible) %>%
  mutate(N = sum(n),
         prop = n / N * 100)
```
