---
title: "HomeOffice_Raw_Processed"
author: "Marton Kovacs"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---

# Loading packages

```{r}
library(tidyverse)
library(jsonlite)
```

# Importing data

```{r}
raw <- read_tsv("Data/Main/Raw/HomeOffice_Main_Raw_data.tsv")
```

# Import survey structure

```{r}
survey_structure <- read_json("HomeOffice_Main.qsf")
```

# Save Qualtrics labels separately

```{r}
labels <- 
  raw %>% 
  slice(1:2)
```

```{r}
raw <- 
  raw %>% 
  slice(-(1:2))
```

# Create participant id

```{r}
raw <- 
  raw %>% 
  rename(participant_id = ResponseId)
```

# Rename variables

```{r}
raw <- 
  raw %>% 
  janitor::clean_names()
```

# Drop trial responses

```{r}
raw <- 
  raw %>% 
  filter(distribution_channel != "preview")
```

# Drop not completed 

```{r}
raw <- 
  raw %>% 
  mutate(progress = as.integer(progress)) %>% 
  filter(progress == 100)
```

# Median time of responding to the survey

```{r}
raw %>% 
  mutate(duration_in_seconds = as.integer(duration_in_seconds)) %>% 
  summarise(median_resp = median(duration_in_seconds) / 60)
```

# Responde date range

```{r}
raw %>% 
  mutate(recorded_date = lubridate::as_datetime(recorded_date)) %>% 
  summarise(min_date = min(recorded_date),
            max_date = max(recorded_date))
```

# Distributon of responses from different sources

```{r}
raw %>%
  group_by(distribution_channel) %>% 
  count()
```

# Merge free text responses with other responses for the same column

```{r}
raw <- 
  raw %>% 
  mutate(area_of_research = case_when(area_of_research == "Other:" ~ area_of_research_6_text,
                                      TRUE ~ area_of_research),
         living_sit = case_when(living_sit == "Other:" ~ living_sit_7_text,
                                      TRUE ~ living_sit),
         need_from_org_11 = case_when(need_from_org_11 == "Other:" ~ need_from_org_11_text,
                                      TRUE ~ need_from_org_11))
```

# Create two variables for the number of children and for their age

```{r}
no_children <- 
  raw %>%
  select(participant_id, contains("children")) %>% 
  gather(key = "age_range", value = "no", -participant_id) %>% 
  mutate(age_range = case_when(age_range == "children_2" ~ "<1",
                               age_range == "children_23" ~ "1-3",
                               age_range == "children_24" ~ "4-6",
                               age_range == "children_25" ~ "7-12",
                               age_range == "children_26" ~ "13-18",
                               age_range == "children_27" ~ "18<"),
         no= as.integer(no),
         no = replace_na(no, 0L)) %>% 
  group_by(participant_id) %>% 
  summarise(number_of_children = sum(no))

raw <- 
  raw %>%
  left_join(., no_children, by = "participant_id")
```

# Drop not needed variables

```{r}
raw <- 
  raw %>% 
  select(-start_date,
         -end_date,
         -distribution_channel,
         -status,
         -progress,
         -finished,
         -recorded_date,
         -duration_in_seconds,
         -user_language,
         -area_of_research_6_text,
         -living_sit_7_text,
         -need_from_org_11_text)
```

# Mutate variables

For the aspects 1 mean at home, and 7 means in the office.

```{r}
raw <- 
  raw %>% 
  mutate_at(vars(contains("home_office_aspect")), ~ case_when(. == "At home\n\n1\n" ~ "1",
                                                             . == "In the office\n7\n" ~ "7",
                                                             TRUE ~ .)) %>% 
  mutate_at(vars(contains("home_office_aspect")), as.integer)
```

# Save data

```{r}
write_tsv(raw, "Data/Main/Processed/HomeOffice_Main_Processed_data.tsv")
```

