---
title: "Researchers working from home"
runtime: shiny
output:
    rmdformats::readthedown:
    highlight: kate
---

```{css, echo = FALSE}
#sidebar {
  background: #A9A9A9;
}

#sidebar a {
  color: #000000;
}

#sidebar a:hover {
  background-color: #828282;
}

#postamble {
  background-color: #828282;
  border-top: #828282;
}
```

```{r setup, echo = FALSE, cache = FALSE, warning = FALSE, message = FALSE}
# Load packages
library(knitr)
library(rmdformats)
library(tidyverse)
library(shiny)

# Global options
options(max.print="75")
opts_chunk$set(echo = FALSE,
	             cache = TRUE,
               prompt = FALSE,
               tidy = TRUE,
               comment = NA,
               message = FALSE,
               warning = FALSE)
opts_knit$set(width = 100)

# Custom ggplot theme
custom_theme <- function() {
  theme_minimal() %+replace%
    theme(
      plot.background = element_rect(fill = "#fcfcfc", colour = NA),
      panel.background = element_blank(),
      axis.title.y = element_text(size = 15, margin = margin(t = 0, r = 10, b = 0, l = 0), angle = 90),
      axis.title.x = element_text(size = 15, margin = margin(t = 10, r = 0, b = 0, l = 0)),
      axis.text = element_text(size = 10),
      strip.text.x = element_text(size = 15)
      )
}

# Import custom funcions
source("R/subset_plot_data.R")
source("R/round_any.R")
```

```{r load data, echo = FALSE, cache = FALSE, warning = FALSE, message = FALSE}
# Create folder structure for the data
# Uncomment the following lines to create the folder structure
# source("R/create_data_structure.R")
# create_data_structure("Data")

# Load data
uni_data <- read_tsv("Data/Main/Processed/HomeOffice_Main_Processed_data.tsv")

# Transform data
uni_data <- 
  uni_data %>% 
  mutate(uni = case_when(uni == "elteppk" ~ "ELTE University PPK",
                         TRUE ~ uni))
```

```{r}
# Available uni choice options
uni_choices <- 
  uni_data %>% 
  distinct(uni) %>% 
  drop_na() %>% 
  pull(uni)

# Select filter
shiny::selectInput("uni", "Choose an institution:",
            choices = c(uni_choices, "All data"),
            selected = "All data",
            width = '300px')

# Filter data
filtered_data <- eventReactive(input$uni, {
  if (input$uni != "All data") {
    uni_data %>% 
      filter(uni == input$uni)
    } else {
      uni_data
      }
  })
```



```{r summary, cache = FALSE}
renderText({
  paste("Data from", count(filtered_data()), "researchers are included in the present report. Out of them,", filter(filtered_data(), working_home_time == "Yes") %>% count(), "have been working more from home during the lockdown compared to the time before.")
})
```

# How efficient they are at doing research from home

# During the lockdown

```{r eff during, cache = FALSE}
renderPlot({
  eff_during_plot_data <-
    filtered_data() %>%
    filter(!is.na(now_before_eff)) %>%
    mutate(now_before_eff = forcats::fct_relevel(now_before_eff, c("less efficient", "similarly efficient","more efficient"))) %>%
    count(now_before_eff) %>%
    mutate(N = sum(n),
           percent = n / N)

  y_max_during <- round_any(max(eff_during_plot_data$percent), 0.1, f = ceiling)

  eff_during_plot_data %>%
    ggplot() +
    aes(x = now_before_eff,
        y = percent) +
    geom_bar(stat = "identity", fill = "#a02043") +
    scale_y_continuous(expand = c(0, 0),
                       labels = scales::percent_format(accuracy = 10L),
                       limits = c(0, y_max_during)) +
    labs(x = "Change in the efficiency of the research work",
         y = "Percentage of responses") +
    custom_theme()
  }, height = 500, width = 800, res = 100)
```

# Expected efficiency after the lockdown - if working more from home

```{r eff after, cache = FALSE}
renderPlot({
  eff_after_plot_data <-
    filtered_data() %>%
    mutate(now_later_eff = forcats::fct_relevel(now_later_eff, c("less efficient", "similarly efficient", "more efficient"))) %>%
    count(now_later_eff) %>%
    mutate(N = sum(n),
           percent = n / N)

  y_max_after <- round_any(max(eff_after_plot_data$percent), 0.1, f = ceiling)

  eff_after_plot_data %>%
    ggplot() +
    aes(x = now_later_eff,
        y = percent) +
    geom_bar(stat = "identity", fill = "#a02043") +
    scale_y_continuous(expand = c(0, 0),
                       labels = scales::percent_format(accuracy = 10L),
                       limits = c(0, y_max_after)) +
    labs(x = "Change in the efficiency of the research work",
         y = "Percentages of responses") +
    custom_theme()
  }, height = 500, width = 800, res = 100)
```

***

# What is more efficient at home and in the office?

```{r aspect summary, cache = FALSE}
aspect_plot_data <- reactive({
  filtered_data() %>%
    select(participant_id, contains("home_office_aspect")) %>%
    gather(key = "aspect", value = "rating", -participant_id) %>% 
    mutate(aspect = case_when(aspect == "home_office_aspect_1" ~ "Optimally organizing my time",
                              aspect == "home_office_aspect_2" ~ "Optimally organizing my tasks",
                              aspect == "home_office_aspect_3" ~ "Keeping focused on my tasks",
                              aspect == "home_office_aspect_4" ~ "Keeping in touch with my team",
                              aspect == "home_office_aspect_5" ~ "Sharing thoughts with colleagues",
                              aspect == "home_office_aspect_6" ~ "Getting support from colleagues",
                              aspect == "home_office_aspect_7" ~ "Working on my manuscript",
                              aspect == "home_office_aspect_8" ~ "Analyzing my data",
                              aspect == "home_office_aspect_9" ~ "Reading the literature",
                              aspect == "home_office_aspect_10" ~ "Collecting data",
                              aspect == "home_office_aspect_11" ~ "Having the infrastructure\n(IT, books, instruments)",
                              aspect == "home_office_aspect_12" ~ "Maintaining emotional balance",
                              aspect == "home_office_aspect_13" ~ "Maintaining work-life balance",
                              aspect == "home_office_aspect_14" ~ "Keeping good relationship\nwith colleagues",
                              aspect == "home_office_aspect_15" ~ "Developing new skills"))
  })

renderPlot({
  aspect_plot_data() %>%
    group_by(aspect) %>%
    summarize(median = median(rating),
              mean = mean(rating)) %>% 
    ggplot() +
    aes(x = fct_reorder(aspect, mean),
        y = mean) +
    geom_bar(stat = "identity", fill = "#a02043") +
    scale_y_continuous(
      expand = c(0, 0.4),
      breaks = c(1, 2, 3, 4, 5, 6, 7),
      labels = c("1\nAt home", "2", "3", "4", "5", "6", "7\nIn the office")) +
    coord_flip(ylim = c(1, 7)) +
    geom_hline(yintercept = 4, linetype = "dashed", color = "#828282", size = 1) +
    labs(x = "Aspects",
         y = "Mean rating") +
    custom_theme()
  }, height = 500, width = 800, res = 100)
```

You can see the distribution of the ratings for each aspect.

```{r aspect input}
aspect_choices <- c("Optimally organizing my time",
                    "Optimally organizing my tasks",
                    "Keeping focused on my tasks",
                    "Keeping in touch with my team",
                    "Sharing thoughts with colleagues",
                    "Getting support from colleagues",
                    "Working on my manuscript",
                    "Analyzing my data",
                    "Reading the literature",
                    "Collecting data",
                    "Having the infrastructure\n(IT, books, instruments)",
                    "Maintaining emotional balance",
                    "Maintaining work-life balance",
                    "Keeping good relationship\nwith colleagues",
                    "Developing new skills")

shiny::selectInput("aspect", "Choose an aspect:",
            choices = aspect_choices,
            width = '300px')
```

```{r aspect individual, cache = FALSE}
renderPlot({
  aspect_individual_plot_data <-
  aspect_plot_data() %>%
  mutate(rating = as_factor(rating)) %>%
  group_by(aspect) %>%
  count(rating, .drop = FALSE)

y_max_aspect <- round_any(max(aspect_individual_plot_data$n), 2, f = ceiling)

  aspect_individual_plot_data %>%
    filter(aspect == input$aspect) %>%
    ggplot() +
    aes(x = rating,
        y = n) +
    geom_bar(stat = "identity", fill = "#a02043") +
    scale_y_continuous(
      expand = c(0, 0),
      limits = c(0, y_max_aspect)) +
    scale_x_discrete(
      breaks = c(1, 2, 3, 4, 5, 6, 7),
      labels = c("1\nAt home", "2", "3", "4", "5", "6", "7\nIn the office")) +
    labs(x = "Rating",
         y = "Count") +
    custom_theme()
}, height = 500, width = 800, res = 100)
```

***

# What proportion of the worktime they used to (red) and would be ideal to (grey) work from home?

```{r feasible input}
shiny::selectInput("feasible", "Is it feasible to work the ideal time from home?",
            choices = c("All responses",
                        "Yes",
                        "No"),
            width = "400px")
```

```{r percentage plot, cache = FALSE}
renderPlot({
  percentage_plot_data <-
    filtered_data() %>%
    select(participant_id,
           prior_home_prop_1,
           future_home_prop_1,
           feasible) %>%
    gather(key = "time", value = "percent", -participant_id, -feasible) %>%
    mutate(time = case_when(time == "prior_home_prop_1" ~ "Prior to pandemic",
                            time == "future_home_prop_1" ~ "Ideal"),
           time = factor(time, c("Prior to pandemic", "Ideal")))

  if(input$feasible == "All responses") {
    percentage_plot_data
  } else {
    percentage_plot_data <-
      percentage_plot_data %>%
      filter(feasible == input$feasible)
  }

  percentage_plot_data %>%
  ggplot() +
  aes(x = percent,
      color = time) +
  geom_density(alpha = 0.6, size = 1) +
  scale_y_continuous(expand = c(0.01, 0),
                     breaks = scales::pretty_breaks()) +
  scale_x_continuous(expand = c(0, 0),
                     breaks = seq(0, 100, 10),
                     labels = seq(0, 100, 10)) +
  scale_fill_manual( values = c('#a02043', '#A9A9A9')) +
  scale_color_manual(values=c('#a02043', '#A9A9A9'))+
  labs(x = "Percentage of worktime working from home",
       y = "Density") +
  custom_theme() +
  theme(legend.position = "none")
}, height = 500, width = 800, res = 100)
```

***

# What would they need from the institution in order to be more efficient and balanced at working from home?

```{r need input, cache = FALSE}
renderPlot({
  need_plot_data <-
    filtered_data() %>%
    select(participant_id, contains("need_from_org"), -need_from_org_11) %>%
    gather(key = "key", value = "need", -participant_id, na.rm = TRUE) %>%
    mutate(need = case_when(need == "Support for problems regarding combining work with family life" ~ "Support for problems\nregarding combining\nwork with family life",
                            need == "Administrative flexibility during lockdowns" ~ "Administrative flexibility\nduring lockdowns",
                            need == "More tips on working from home" ~ "More tips on\nworking from home",
                            TRUE ~ need)) %>%
    count(need)

  y_max_need <- round_any(max(need_plot_data$n), 2, f = ceiling)

  need_plot_data %>%
    ggplot() +
    aes(x = reorder(need, -n),
        y = n) +
    geom_bar(stat = "identity", fill = "#a02043") +
    scale_y_continuous(
      limits = c(0, y_max_need),
      expand = c(0, 0)) +
    coord_flip() +
    labs(x = "Needs",
         y = "Number of responses") +
    custom_theme()
  }, height = 500, width = 800, res = 100)
```

_Note: The figure could contain multiple responses from one respondent._

***

# Seeing subsets of responses for the efficiency of working from home during and after lockdown
# Gender

```{r gender input}
shiny::selectInput("gender", "Choose a subset:",
            choices = c("Female",
                        "Male"),
            width = "400px")
```

```{r gender plot, cache = FALSE}
renderPlot({
  subset_gender_plot_data <-
    subset_plot_data(data = filtered_data(),
                     filter_var = gender,
                     output_type = "percent")

  y_max_gender <- round_any(max(subset_gender_plot_data$percent), 0.1, f = ceiling)

  subset_gender_plot_data %>%
    filter(gender == input$gender) %>%
    ggplot() +
    aes(x = rating,
        y = percent) +
    geom_bar(stat = "identity", fill = "#a02043") +
    facet_wrap(. ~ time) +
    scale_y_continuous(expand = c(0, 0),
                       limits = c(0, y_max_gender),
                       labels = scales::percent_format(accuracy = 10L)) +
    labs(x = "Change in the efficiency of the research work",
         y = "Percentage") +
    custom_theme()
}, height = 500, width = 800, res = 100)
```

# Living situation

```{r living input, cache = FALSE}
renderUI({
living_sit_filter <-
  filtered_data() %>%
    count(living_sit) %>%
    filter(n > 10) %>% 
    pull(living_sit)

  shiny::selectInput("living_sit", "Choose a subset:",
                     choices = living_sit_filter,
                     width = "400px")
  })
```

```{r living plot, cache = FALSE}
renderPlot({
  subset_living_plot_data <-
    subset_plot_data(data = filtered_data(),
                     filter_var = living_sit,
                     output_type = "percent") %>%
    filter(N > 10)

  y_max_living <- round_any(max(subset_living_plot_data$percent), 0.1, f = ceiling)

  subset_living_plot_data %>%
    filter(living_sit == input$living_sit) %>%
    ggplot() +
    aes(x = rating,
        y = percent) +
    geom_bar(stat = "identity", fill = "#a02043") +
    facet_wrap(. ~ time) +
    scale_y_continuous(expand = c(0, 0),
                       labels = scales::percent_format(accuracy = 10L),
                       limits = c(0, y_max_living)) +
    labs(x = "Change in the efficiency of the research work",
         y = "Percentage") +
    custom_theme()
}, height = 500, width = 800, res = 100)
```

# Homeschool

Subsets of the results based on whether the respondent had to do home-schooling during the present pandemic.

```{r homeschool input}
shiny::selectInput("homeschool", "Choose a subset:",
            choices = c("Yes", "No"),
            width = "400px")
```

```{r homeschool plot, cache = FALSE}
renderPlot({
    subset_homeschool_data <-
    subset_plot_data(data = filtered_data(),
                     filter_var = homeschool,
                     output_type = "percent")

  y_max_homeschool <- round_any(max(subset_homeschool_data$percent), 0.1, f = ceiling)

  subset_homeschool_data %>%
    filter(homeschool == input$homeschool) %>%
    ggplot() +
    aes(x = rating,
        y = percent) +
    geom_bar(stat = "identity", fill = "#a02043") +
    facet_wrap(. ~ time) +
    scale_y_continuous(expand = c(0, 0),
                       labels = scales::percent_format(accuracy = 10L),
                       limits = c(0, y_max_homeschool)) +
    labs(x = "Change in the efficiency of the research work",
         y = "Percentage") +
    custom_theme()
}, height = 500, width = 800, res = 100)
```

