---
title: "HomeOffice_Sampling"
author: "Marton Kovacs"
output: html_document
---

# Load packages

```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(readxl)
library(writexl)
```

# Import data

We used a scraping code to collect meta information of published articles in the Science Direct database.

```{r, message = FALSE, warning = FALSE}
email <- read_csv("Data/Sample/HomeOffice_Sample_Mail.csv",
                  locale = locale(encoding = "UTF-8"))
```

The list of journals and their subfields at the time of the data collection.

```{r, message = FALSE}
journal <- read_csv2("Data/Sample/HomeOffice_Sample_Journal.csv",
                     locale = locale(encoding = "ISO-8859-13"))
```

Some of these email addresses were used in a different project. We downloaded the used email addresses from the Qualtrics mail sender history and merged them (there were different batches).

```{r}
used <- read_xlsx("Data/Sample/HomeOffice_Sample_Used.xlsx")
```

Load previously used batches.

These batches were used for the pilot survey:

```{r}
batch_1 <- read_xlsx("Data/Sample/HomeOffice_Sample_Batch_1.xlsx")
```

```{r}
batch_2 <- read_xlsx("Data/Sample/HomeOffice_Sample_Batch_2.xlsx")
```

# Descriptives

We have downloaded the meta-information of `r email %>% distinct(doi) %>% filter(!is.na(doi)) %>% count()` individual articles.

We could extract the email addresses of `r email %>% distinct(email) %>% filter(!is.na(email)) %>% count()` corresponding authors of these articles. This does not mean that all email addresses are working as the automatized scraper code could make mistakes.

At the time of our data collection there were `r journal %>% distinct(publicationname) %>% count()` journals in the Science Direct database.

# Variable transformation

```{r}
used <-
  used %>% 
  rename(surname = LastName,
         email = Email)
```

# Filtering the email addresses
## Drop empty email address cells

```{r}
email <- 
  email %>% 
  filter(!is.na(email))
```

## Drop empty last name cells

```{r}
email <- 
  email %>% 
  filter(!is.na(surname))
```

## Drop duplicate email addresses

```{r}
email <- 
  email %>% 
  distinct(email, .keep_all = T)
```

## Exrtacting parenthases from the email addresses

```{r}
email <- 
  email %>% 
  mutate(email = str_to_lower(email),
         email = str_remove_all(email, "\\(|\\)"))
```

## Checking valid email addresses

```{r}
email <- 
  email %>% 
  mutate(email_valid = str_detect(email, "([_+a-z0-9-]+(\\.[_+a-z0-9-]+)*@[a-z0-9-]+(\\.[a-z0-9-]+)*(\\.[a-z]{2,14}))"))
```

There are `r email %>% filter(email_valid == TRUE) %>% count()` valid email addresses.

## Keep only valid email addresses

```{r}
email <- 
  email %>% 
  filter(email_valid == TRUE)
```

There are `r email %>% count()` email addresses left.

## Delete used email addresses from the list

Comparing the two list. In some cases there can be an inconsistency as the email addresses in the other study were complemented by hand.

```{r}
used_additional <-
  used %>% 
  anti_join(., email, by = c("surname", "email"))
```

Deleting used addresses.

```{r}
email <-
  email %>% 
  anti_join(., used, by = c("surname", "email"))
```

There are `r email %>% count()` email addresses left.

```{r}
email <-
  email %>% 
  anti_join(., batch_1, by = c("surname", "email"))
```

```{r}
email <-
  email %>% 
  anti_join(., batch_2, by = c("surname", "email"))
```

# Choose only needed variables

```{r}
email <-
  email %>% 
  select(surname,
         email)
```

# Make a random selection of emails

```{r}
# First batch selection
first_batch <-
  email %>% 
  sample_n(500) 
```

```{r}
# Second batch selection
second_batch <-
  email %>% 
  sample_n(2500) 
```

```{r}
# Third batch selection
third_batch <-
  email %>% 
  sample_n(10000) 
```

# Save random selection of emails

```{r}
## First batch selection
write_xlsx(first_batch, "Data/Sample/HomeOffice_Sample_Batch_1.xlsx")

## Second batch selection
write_xlsx(second_batch, "Data/Sample/HomeOffice_Sample_Batch_2.xlsx")

## Second batch selection
write_xlsx(third_batch, "Data/Sample/HomeOffice_Sample_Batch_3.xlsx")
```