---
title: "Researchers working from home at ELTE PPK"
runtime: shiny
output:
    rmdformats::readthedown:
    highlight: kate
---

```{css, echo = FALSE}
#sidebar {
  background: #A9A9A9;
}

#sidebar a {
  color: #000000;
}

#sidebar a:hover {
  background-color: #828282;
}

#postamble {
  background-color: #828282;
  border-top: #828282;
}
```

```{r setup, echo = FALSE, cache = FALSE, warning = FALSE, message = FALSE}
# Load packages
library(knitr)
library(rmdformats)
library(tidyverse)

# Global options
options(max.print="75")
opts_chunk$set(echo = FALSE,
	             cache = TRUE,
               prompt = FALSE,
               tidy = TRUE,
               comment = NA,
               message = FALSE,
               warning = FALSE)
opts_knit$set(width = 100)

# Custom ggplot theme
custom_theme <- function() {
  theme_minimal() %+replace%
    theme(
      plot.background = element_rect(fill = "#fcfcfc", colour = NA),
      panel.background = element_blank(),
      axis.title.y = element_text(size = 15, margin = margin(t = 0, r = 10, b = 0, l = 0), angle = 90),
      axis.title.x = element_text(size = 15, margin = margin(t = 10, r = 0, b = 0, l = 0)),
      axis.text = element_text(size = 10),
      strip.text.x = element_text(size = 15)
      )
}

# Import custom funcions
source("R/subset_plot_data.R")
source("R/round_any.R")
```

```{r load data, echo = FALSE, cache = FALSE, warning = FALSE, message = FALSE}
# Create folder structure for the data
# Uncomment the following lines to create the folder structure
# source("R/create_data_structure.R")
# create_data_structure("Data")

# Load data
uni_data <- read_tsv("Data/Main/Processed/HomeOffice_Main_Processed_data.tsv")
```

From ELTE PPK `r count(uni_data)` researchers responded to the questionnaire. Out of them, `r filter(uni_data, working_home_time == "Yes") %>% count()` have been working more from home during the lockdown compared to the time before.

# How efficient they are at doing research from home

# During the lockdown

```{r eff during}
eff_during_plot_data <- 
  uni_data %>% 
  filter(!is.na(now_before_eff)) %>%
  mutate(now_before_eff = forcats::fct_relevel(now_before_eff, c("less efficient", "similarly efficient","more efficient"))) %>% 
  count(now_before_eff) %>% 
  mutate(N = sum(n),
         percent = n / N)

y_max_during <- round_any(max(eff_during_plot_data$percent), 0.1, f = ceiling)

eff_during_plot_data %>% 
  ggplot() +
  aes(x = now_before_eff,
      y = percent) +
  geom_bar(stat = "identity", fill = "#a02043") +
  scale_y_continuous(expand = c(0, 0),
                     labels = scales::percent_format(accuracy = 10L),
                     limits = c(0, y_max_during)) +
  labs(x = "Change in the efficiency of the research work",
       y = "Percentage of responses") +
  custom_theme()
```

# Expected efficiency after the lockdown - if working more from home

```{r eff after}
eff_after_plot_data <- 
  uni_data %>% 
  mutate(now_later_eff = forcats::fct_relevel(now_later_eff, c("less efficient", "similarly efficient", "more efficient"))) %>%
  count(now_later_eff) %>% 
  mutate(N = sum(n),
         percent = n / N)

y_max_after <- round_any(max(eff_after_plot_data$percent), 0.1, f = ceiling)

eff_after_plot_data %>% 
  ggplot() +
  aes(x = now_later_eff,
      y = percent) +
  geom_bar(stat = "identity", fill = "#a02043") +
  scale_y_continuous(expand = c(0, 0),
                     labels = scales::percent_format(accuracy = 10L),
                     limits = c(0, y_max_after)) +
  labs(x = "Change in the efficiency of the research work",
       y = "Percentages of responses") +
  custom_theme()
```

***

# What is more efficient at home and in the office?

```{r aspect summary}
aspect_plot_data <- 
  uni_data %>% 
  select(participant_id, contains("home_office_aspect")) %>% 
  gather(key = "aspect", value = "rating", -participant_id) %>% 
  mutate(aspect = case_when(aspect == "home_office_aspect_1" ~ "Optimally organizing my time",
                            aspect == "home_office_aspect_2" ~ "Optimally organizing my tasks",
                            aspect == "home_office_aspect_3" ~ "Keeping focused on my tasks",
                            aspect == "home_office_aspect_4" ~ "Keeping in touch with my team",
                            aspect == "home_office_aspect_5" ~ "Sharing thoughts with colleagues",
                            aspect == "home_office_aspect_6" ~ "Getting support from colleagues",
                            aspect == "home_office_aspect_7" ~ "Working on my manuscript",
                            aspect == "home_office_aspect_8" ~ "Analyzing my data",
                            aspect == "home_office_aspect_9" ~ "Reading the literature",
                            aspect == "home_office_aspect_10" ~ "Collecting data",
                            aspect == "home_office_aspect_11" ~ "Having the infrastructure\n(IT, books, instruments)",
                            aspect == "home_office_aspect_12" ~ "Maintaining emotional balance",
                            aspect == "home_office_aspect_13" ~ "Maintaining work-life balance",
                            aspect == "home_office_aspect_14" ~ "Keeping good relationship\nwith colleagues",
                            aspect == "home_office_aspect_15" ~ "Developing new skills"))

aspect_summary_plot_data <- 
  aspect_plot_data %>% 
  group_by(aspect) %>% 
  summarize(median = median(rating),
            mean = mean(rating))

aspect_summary_plot_data %>% 
  ggplot() +
  aes(x = fct_reorder(aspect, mean),
      y = mean) +
  geom_bar(stat = "identity", fill = "#a02043") +
  scale_y_continuous(
    expand = c(0, 0.4),
    breaks = c(1, 2, 3, 4, 5, 6, 7),
    labels = c("1\nAt home", "2", "3", "4", "5", "6", "7\nIn the office")) +
  coord_flip(ylim = c(1, 7)) +
  geom_hline(yintercept = 4, linetype = "dashed", color = "#828282", size = 1) +
  labs(x = "Aspects",
       y = "Mean rating") +
  custom_theme()
```

You can see the distribution of the ratings for each aspect.

```{r aspect input}
shiny::selectInput("aspect", "Choose an aspect:",
            choices = pull(aspect_summary_plot_data, aspect),
            width = '300px')
```

```{r aspect individual, cache = FALSE}
aspect_individual_plot_data <- 
  aspect_plot_data %>% 
  mutate(rating = as_factor(rating)) %>% 
  group_by(aspect) %>% 
  count(rating, .drop = FALSE)
    
  
y_max_aspect <- round_any(max(aspect_individual_plot_data$n), 2, f = ceiling)

renderPlot({
  aspect_individual_plot_data %>% 
    filter(aspect == input$aspect) %>% 
    ggplot() +
    aes(x = rating,
        y = n) +
    geom_bar(stat = "identity", fill = "#a02043") +
    scale_y_continuous(
      expand = c(0, 0),
      limits = c(0, y_max_aspect)) +
    scale_x_discrete(
      breaks = c(1, 2, 3, 4, 5, 6, 7),
      labels = c("1\nAt home", "2", "3", "4", "5", "6", "7\nIn the office")) +
    labs(x = "Rating",
         y = "Count") +
    custom_theme()
}, height = 500, width = 800, res = 100)
```

***

# What proportion of the worktime they used to (red) and would be ideal to (grey) work from home?

```{r feasible input}
shiny::selectInput("feasible", "Is it feasible to work the ideal time from home?",
            choices = c("All responses",
                        "Yes",
                        "No"),
            width = "400px")
```

```{r percentage plot, cache = FALSE}
percentage_plot_data <- 
  uni_data %>% 
  select(participant_id,
         prior_home_prop_1,
         future_home_prop_1,
         feasible) %>% 
  gather(key = "time", value = "percent", -participant_id, -feasible) %>% 
  mutate(time = case_when(time == "prior_home_prop_1" ~ "Prior to pandemic",
                          time == "future_home_prop_1" ~ "Ideal"),
         time = factor(time, c("Prior to pandemic", "Ideal")))

renderPlot({
  if(input$feasible == "All responses") {
    percentage_plot_data
  } else {
    percentage_plot_data <-
      percentage_plot_data %>%
      filter(feasible == input$feasible)
  }
  
  percentage_plot_data %>% 
  ggplot() +
  aes(x = percent,
      color = time) +
  geom_density(alpha = 0.6, size = 1) +
  scale_y_continuous(expand = c(0.01, 0),
                     breaks = scales::pretty_breaks()) +
  scale_x_continuous(expand = c(0, 0),
                     breaks = seq(0, 100, 10),
                     labels = seq(0, 100, 10)) +
  scale_fill_manual( values = c('#a02043', '#A9A9A9')) +
  scale_color_manual(values=c('#a02043', '#A9A9A9'))+
  labs(x = "Percentage of worktime working from home",
       y = "Density") +
  custom_theme() +
  theme(legend.position = "none")
}, height = 500, width = 800, res = 100)
```

***

# What would they need from the institution in order to be more efficient and balanced at working from home?

```{r need input}
need_plot_data <- 
  uni_data %>% 
  select(participant_id, contains("need_from_org"), -need_from_org_11) %>% 
  gather(key = "key", value = "need", -participant_id, na.rm = TRUE) %>% 
  mutate(need = case_when(need == "Support for problems regarding combining work with family life" ~ "Support for problems\nregarding combining\nwork with family life",
                          need == "Administrative flexibility during lockdowns" ~ "Administrative flexibility\nduring lockdowns",
                          need == "More tips on working from home" ~ "More tips on\nworking from home",
                          TRUE ~ need)) %>%
  count(need)

y_max_need <- round_any(max(need_plot_data$n), 2, f = ceiling)
```

```{r need plot}
need_plot_data %>% 
  ggplot() +
  aes(x = reorder(need, -n),
      y = n) +
  geom_bar(stat = "identity", fill = "#a02043") +
  scale_y_continuous(
    limits = c(0, y_max_need),
    expand = c(0, 0)) +
  coord_flip() +
  labs(x = "Needs",
       y = "Number of responses") +
  custom_theme()
```

_Note: The figure could contain multiple responses from one respondent._

***

# Seeing subsets of responses for the efficiency of working from home during and after lockdown
# Gender

```{r gender input}
shiny::selectInput("gender", "Choose a subset:",
            choices = c("Female",
                        "Male"),
            width = "400px")
```

```{r gender plot, cache = FALSE}
subset_gender_plot_data <- 
  subset_plot_data(data = uni_data,
                   filter_var = gender,
                   output_type = "percent")

y_max_gender <- round_any(max(subset_gender_plot_data$percent), 0.1, f = ceiling)

renderPlot({
  subset_gender_plot_data %>% 
    filter(gender == input$gender) %>% 
    ggplot() +
    aes(x = rating,
        y = percent) +
    geom_bar(stat = "identity", fill = "#a02043") +
    facet_wrap(. ~ time) +
    scale_y_continuous(expand = c(0, 0),
                       limits = c(0, y_max_gender),
                       labels = scales::percent_format(accuracy = 10L)) +
    labs(x = "Change in the efficiency of the research work",
         y = "Percentage") +
    custom_theme()
}, height = 500, width = 800, res = 100)
```

# Living situation

```{r living input}
living_sit_filter <- 
  uni_data %>% 
  count(living_sit) %>% 
  filter(n > 10)

shiny::selectInput("living_sit", "Choose a subset:",
            choices = pull(living_sit_filter, living_sit),
            width = "400px")
```

```{r living plot, cache = FALSE}
subset_living_plot_data <- 
  subset_plot_data(data = uni_data,
                   filter_var = living_sit,
                   output_type = "percent") %>% 
  filter(N > 10)

y_max_living <- round_any(max(subset_living_plot_data$percent), 0.1, f = ceiling)

renderPlot({
  subset_living_plot_data %>% 
    filter(living_sit == input$living_sit) %>% 
    ggplot() +
    aes(x = rating,
        y = percent) +
    geom_bar(stat = "identity", fill = "#a02043") +
    facet_wrap(. ~ time) +
    scale_y_continuous(expand = c(0, 0),
                       labels = scales::percent_format(accuracy = 10L),
                       limits = c(0, y_max_living)) +
    labs(x = "Change in the efficiency of the research work",
         y = "Percentage") +
    custom_theme()
}, height = 500, width = 800, res = 100)
```

# Homeschool

Subsets of the results based on whether the respondent had to do home-schooling during the present pandemic.

```{r homeschool input}
shiny::selectInput("homeschool", "Choose a subset:",
            choices = c("Yes", "No"),
            width = "400px")
```

```{r homeschool plot, cache = FALSE}
subset_homeschool_data <- 
  subset_plot_data(data = uni_data,
                   filter_var = homeschool,
                   output_type = "percent")

y_max_homeschool <- round_any(max(subset_homeschool_data$percent), 0.1, f = ceiling)

renderPlot({
  subset_homeschool_data %>% 
    filter(homeschool == input$homeschool) %>% 
    ggplot() +
    aes(x = rating,
        y = percent) +
    geom_bar(stat = "identity", fill = "#a02043") +
    facet_wrap(. ~ time) +
    scale_y_continuous(expand = c(0, 0),
                       labels = scales::percent_format(accuracy = 10L),
                       limits = c(0, y_max_homeschool)) +
    labs(x = "Change in the efficiency of the research work",
         y = "Percentage") +
    custom_theme()
}, height = 500, width = 800, res = 100)
```

